% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

%\usepackage[english]{babel}
%\usepackage{amsmath}
%\usepackage{amsthm}
%\usepackage{enumerate}
%\usepackage{graphicx}
%\usepackage{mathrsfs}
%%\usepackage{easymat}
%%\usepackage{geometry}
%%\usepackage{showlabels}
%%\usepackage{backref}
%%\usepackage{microtype}
%\usepackage{amssymb}
%\usepackage[usenames,dvipsnames]{color}
%\usepackage{empheq}
%%\usepackage{showkeys}
\usepackage{hyperref}
%%\hypersetup{
%%colorlinks = true, 
%%linkcolor = {blue}
%%}
%\usepackage[affil-it]{authblk}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

%\long\def\symbolfootnote[#1]#2{\begingroup%
%\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

\begin{document} 
 
\name{MANUELA GIROTTI\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Colorado State University}\\
Department of Mathematics \\
1874 Campus Delivery \\
Fort Collins, CO 80523, USA \\
}
\address{
\\
\\
%\hfill Date of birth: 17th January 1986\\
%\hfill Nationality: Italian\\
\hfill tel. : (+1) 970-491-0725\\
\hfill e-mail: \texttt{Manuela.Girotti@colostate.edu}}%\href{mailto:manuela.girotti@uclouvain.be}{manuela.girotti@uclouvain.be}}

 
\begin{resume} 

 \section{Status}
 
 {\bf Italy} - citizen  \\
 {\bf Canada} - permanent resident \hfill since 05/2017 \\
 {\bf United States} - H1-B visa worker \hfill 01/2017--12/2019

 
 \section{Current position}
  {\bf Department of Mathematics} \\
 Colorado State University, Fort Collins, CO \\
 Postdoctoral Fellow \hfill 01/2017--12/2019 
 
  {\bf Department of Mathematics and Statistics} \\
 Concordia University, Montr\'eal, Qu\'ebec, Canada \\
Affiliate Assistant Professor \hfill 10/2017--09/2020



 \section{Past position}
  {\bf Institut de Recherche en Math\'ematique et Physique} \\
 Universit\'e Catholique de Louvain, Louvain-la-neuve, Belgium \\
Postdoctoral Fellow / Assistante de recherche \hfill 11/2014--10/2016 \\



\section{Education}

{\bf Concordia University}, Montr\'eal, Qu\'ebec, Canada \hfill 2010--2014 \\
 Ph.D. in Mathematics, supervisor Dr. Marco Bertola\\
 Thesis title: \emph{``Riemann-Hilbert approach to Gap Probabilities of Determinantal Point Processes"}. \\
 %Date and time: 27/8/2014, Montr\'eal. 
 External examiner: Dr. Alexander R. Its (IUPUI). Thesis ranking: excellent.

{\bf Universit\`a degli Studi di Milano}, Milan, Italy \hfill 2008--2010 \\
 Laurea Magistrale (M.Sc.) in Mathematics, 110/110 \emph{cum laude}\footnote{Performance in the final examination is graded from 66 to 110. A \emph{cum laude} can be added to the maximum grade as a special distinction.} \\
 supervisor Dr. Elisabetta Rocca \\
 Thesis title: \emph{``Time relaxation of a phase-field model with entropy balance''}.
 
 {\bf Universit\`a degli Studi di Milano}, Milan, Italy \hfill 2005--2008 \\
 Laurea Triennale (B.Sc.) in Mathematics, 110/110 \emph{cum laude}$^\ast$ \\
supervisor Dr. Dietmar Klemm \\
 Thesis title: \emph{``Dirac's  magnetic monopole''}.
 
 
 {\bf Liceo Classico Valsalice}, Turin, Italy \hfill 2000--2005 \\
 Maturit\`a classica (high school diploma), 100/100 \\
 Project title: \emph{``Turris Babel''}. \\
 
  \section{Qualifications}
  
 \emph{Qualifi\'ee aux fonctions de Ma\^itre de Conf\'erence} \hfill 02/2016--12/2020 \\
%n$^\circ$ de qualification 16225290032, 
Section 25 - Math\'ematiques \\
Minist\`ere de l'\'Education nationale, de l'Enseignement sup\'erieur et de la Recherche, France.   \\

% \emph{Certificat de S\'election du Qu\'ebec (CSQ)} \hfill 05/2016\\
% Programme de l'exp\'erience qu\'eb\'ecoise (PEQ) - Dipl\^om\'ee du Qu\'ebec \\
%Minist\`ere de l'Immigration, de la Diversit\'e et de l'Inclusion, Qu\'ebec, Canada. \\

 
   \section{Publications}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item[-] M. Girotti, ``Vanishing time-relaxation for a phase-field model with entropy balance", \emph{Adv. Math. Sci. Appl.}, 22(\textbf{2}), 553-575, 2012. 
\item[-] M. Girotti, ``Riemann-Hilbert approach to gap probabilities for the Generalized Bessel process", \emph{Math. Phys. Anal. Geom.} \textbf{17} (1), 183-211, 2014.
\item[-] M. Girotti, ``Asymptotics of the Tacnode process: a transition between the gap probabilities from the Tacnode to the Airy process", \emph{Nonlinearity} \textbf{27}, 1937-1968, 2014.
\item[-] M. Girotti, ``Riemann-Hilbert approach to gap probabilities for the Bessel process", \emph{Phys. D}, 295-296C, 103-121, 2015.
\item[-] T. Claeys, M. Girotti, D. Stivigny, ``Large gap asymptotics at the hard edge for product random matrices and Muttalib-Borodin ensembles", \emph{Internat. Math. Res. Notices}, rnx202, 2017. 
\item[-] M. Girotti, T. Grava, K. McLaughlin, ``Rigorous asymptotics of a KdV soliton gas", submitted, 2018.\\
 \end{itemize}

 
 \section{Affiliations}
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item[-] {\bf 2010--2011:} member of Italian National Group for Mathematical Analysis, Probability and their Applications (GNAMPA). 
\item[-] {\bf 2010--2014 and 2017-2018:} member of American Mathematical Society (AMS).
\item[-] {\bf 2011--2014:} member of the organization Italian Scientific Community in Canada - Qu\'ebec section (CSIC).
 \item[-] {\bf 2014--2016:} member of Interuniversity Attraction Poles - Dynamics, Geometry and Statistical Physics (DYGEST).
 \item[-] {\bf 2014--2016:} member of the ERC projet ``Critical phenomena in random matrix theory and integrable systems" (CRaMIS), principal investigator Dr. Tom Claeys. 
 \item[-] {\bf 2017--2018:} member of the International Presidential Fellow program, Colorado State University.\\
 \end{itemize}
 
 \section{Scholarships and awards (selection)}
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item[-] Borsa di studio SKF (high school scholarship), SKF Industrie S.p.A., a.y. 2000--2005.
 \item[-] 2$^{\rm nd}$ qualified for Certamen Taurinense  (Latin literature competition), Torino, May 2005;
\item[-] Fondo per il sostegno dei giovani e per favorire la mobilit\`a degli studenti (tuition fee remission), Universit\`a degli Studi di Milano, 2005--2007.
\item[-] Faculty of Arts\&Science Graduate Fellowship, Concordia University, 2010--2013.
\item[-] Concordia University Partial Tuition Graduate Scholarship for International Students, Concordia University, 2010--2011.
\item[-] ISM Scholarship, Institut des Sciences Math\'ematiques, Montr\'eal, 2011--2012.
%\item[-] ISM Travel Scholarship, Institut des Sciences Math\'ematiques, Montr\'eal, June 2011;
\item[-] Exemption des frais de scolarit\'e suppl\'ementaires (MEQ), Minist\`ere de l'\'Education, du Loisir et du Sport du Qu\'ebec, 2011--2013.
\item[-] Concordia Merit Scholarship, Concordia University, 2012--2013.
%\item[-] Campaign for a New Millennium Graduate Scholarship - Faculty of Arts\&Science, Concordia University, 2013-2014.
\item[-] Concordia Accelerator Award, Concordia University, 2014. \\
 \end{itemize}
 
 
  \section{Visits}
 \begin{itemize} \itemsep -2pt  % reduce space between items 
\item[-] June 2012 (30 days), \emph{PIMS-Mprime Summer School in Probability}, University of British Columbia (Canada);
\item[-] March 2014 (5 days), Universit\'e catholique de Louvain (Belgium), upon invitation of Prof. Tom Claeys;
\item[-] May 2015 (5 days) and February 2016 (3 days), Universit\'e d'Angers (France), upon invitation of Prof. Mattia Cafasso, ;
\item[-] June 2017 (5 days), SISSA (Italy), upon invitation of Prof. Marco Bertola and Prof. Tamara Grava;  
\item[-] May 2018 (5 days), Universit\'e catholique de Louvain (Belgium), upon invitation of Prof. Tom Claeys;
\item[-] June 2018 (5 days), SISSA (Italy), upon invitation of Prof. Tamara Grava.  \\
 \end{itemize}

% \section{Research interests}
%\ Random matrices, Integrable Systems, Riemann-Hilbert problems.
 
 
  \section{Talks (selection)}
 \begin{itemize} \itemsep -2pt  % reduce space between items
% \item[-] \emph{Time relaxation of a phase-field model with entropy balance}, 02-2011, seminar at Concordia University, Montr\'eal (Canada).
 \item[-] \emph{A Peek into the Math world: from abstraction to applications}, 11/2012, invited talk at Institut Italien de Culture de Montr\'eal, Montr\'eal (Canada).
 \item[-] \emph{Riemann-Hilbert approach to gap probabilities for the Bessel process}, poster presentation at the conference ``Advanced School and Workshop on Random Matrices and Growth Models", 09/2013, ICTP, Trieste (Italy).
% \item[-] \emph{Gap probabilities for the Generalized Bessel process: a Riemann-Hilbert approach}, Working Seminar Mathematical Physics, 03-10-2013, Concordia University, Montr\'eal (Canada).
% \item[-] \emph{Curve flows and solitons equations: the vortex filament case}, 29-11-2013, Concordia University, Montr\'eal (Canada).
% \item[-] \emph{Gap probabilities and Isomonodromic $\tau$-function: from integrable systems to non-intersecting Brownian motion}, 12-2013, seminar at Universit\`a degli Studi Milano-Bicocca, Milan (Italy).
% \item[-] \emph{Gap Probabilities of the Tacnode process}, 09-2014, talk at Centre de Recherche Math\'ematiques (CRM), Montr\'eal (Canada).
%\item[-] \emph{Riemann-Hilbert approach to Gap Probabilities of Determinantal Point Processes}, 01-2015, seminar at KU Leuven, Leuven (Belgium);
 \item[-] \emph{Gap Probabilities of the Tacnode process}, poster presentation at the conference ``Asymptotics in integrable systems, random matrices and random processes and universality. In honour of Percy Deift's 70th birthday", 06/2015, CRM, Montr\'eal (Canada).
%\item[-] \emph{Smallest singular value distribution and large gap asymptotics for products of random matrices}, poster presentation at the workshop ``XI Brunel-Bielefeld Workshop on Random Matrix Theory and Applications", 12/2015, ZiF - Universit\"{a}t Bielefeld, Bielefeld (Germany).
\item[-] \emph{Smallest singular value distribution and large gap asymptotics for products of random matrices}, invited talk at the workshop ``Six-vertex model, dimers, shapes, and all that", 03/2016, Simons Center for Geometry and Physics, Stony Brook University (NY, USA).
\item[-] \emph{``Integrable" gap probabilities for the Generalized Bessel process}, invited talk at the workshop ``Painlev\'e Equations and Discrete Dynamics", 10/2016, Banff International Research Station, Banff (AB, Canada).
\item[-] \emph{Smallest singular value distribution and large gap asymptotics for products of random matrices}, talk at the 14th International Symposium on Orthogonal Polynomials, Special Functions and Applications (OPSFA14), 07/2017, University of Kent, Canterbury (UK). 
\item[-] \emph{Integrable gap probabilities for the Generalized Bessel process}, invited talk at the workshop ``Painlev\'e Equations and Applications: A Workshop in Memory of A. A. Kapaev", 08/2017, Michigan Center for Applied and Interdisciplinary Mathematics (MCAIM), Ann Arbor (MI, USA).
\item[-] \emph{Rigorous asymptotics of the soliton gas}, invited talk to the special session on Probabilistic Models in Mathematical Physics, AMS Spring Meeting, 04/2018, Vanderbilt University, Nashville (TN, USA).
\\
 \end{itemize}
 
 \section{Invited conferences}
\begin{itemize}\itemsep -2pt
\item[-] \emph{FroM-PDE: Frobenius Manifolds and Hamiltonian Partial Differential Equations}, SISSA, Trieste (Italy), September 2013;
\item[-] \emph{Integrable Systems, Random Matrices and Combinatorics. Nicholas Ercolani's 60th Birthday}, University of Arizona, Tucson (AZ, USA), October 2013;
\item[-] \emph{Scattering and Inverse Scattering in Multidimensions}, University of Kentucky, Lexington (KY, USA), May 2014;
\item[-] \emph{Asymptotics in integrable systems, random matrices, random processes and universality}, Centre de Recherches Mat\'ematiques, Montr\'eal (QC, Canada), June 2015;
\item[-] \emph{Probability and asymptotic analysis in strongly coupled systems}, Hausdorff Center for Mathematics, Bonn (Germany), January 2016;
\item[-] \emph{Six-vertex model, dimers, shapes, and all that}, Simons Center for Geometry and Physics, Stony Brook University (NY, USA), March 2016;
\item[-] \emph{Painlev\'e Equations and Discrete Dynamics}, Banff International Research Station, Banff (AB, Canada), October 2016;
\item[-] \emph{Random Matrices and Determinantal Process}, Centre International de Rencontres Math\'ematiques (CIRM), Luminy-Marseille (France), March 2017;
\item[-] \emph{Geometry of Integrable systems}, SISSA, Trieste (Italy), June 2017; 
\item[-] \emph{Critical phenomena for random matrices and integrable systems}, Ch\^{a}teau de Limelette (Belgium), June 2017;
\item[-] \emph{Painlev\'e Equations and Applications:  A Workshop in Memory of A. A. Kapaev}, Michigan Center for Applied and Interdisciplinary Mathematics (MCAIM), Ann Arbor (MI, USA), August 2017;
\item[-] \emph{Joint Mathematics Meetings}, special session on Algebraic, Analytic, and Geometric Aspects of Integrable Systems, Painlev\'e Equations, and Random Matrices, San Diego (CA, USA), January 2018
\item[-] \emph{AMS Spring Southeastern Section Meeting }, special session on Probabilistic Models in Mathematical Physics, Nashville (TN, USA), April 2018. \\
\end{itemize}

%\section{Participation to conferences}
%\begin{itemize} \itemsep -2pt
%\item[-] \emph{The 13th International Symposium on Orthogonal Polynomials, Special Functions and Applications}, Gaithersburg (MD, USA), June 2015;
%\item[-] \emph{Advanced School and Workshop on Random Matrices and Growth Models}, ICTP, Miramare (Italy), September 2013;
%%\item[-] \emph{CMS Winter Meeting}, Canadian Mathematical Society, Montr\'eal (QC, Canada), December 2012;
%\item[-] \emph{Winter School GranMA 2012 - Random Matrices and Integrable Systems}, \'Ecole de Physique des Houches, Les Houches (France), March 2012;
%\item[-] \emph{Interfaces and discontinuities in solids, liquids and crystals - INDI2011}, Palazzo Feltrinelli, Gargnano (Italy), June 2011;
%\item[-] \emph{The Versatility of Integrability. Celebrating Igor Krichever's 60th Birthday}, Columbia University, New York (NY, USA), May 2011.
%\end{itemize}



  \section{Teaching activities}
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item[-] instructor of MATH 530 - Mathematics for Scientists and Engineers,  Colorado State University, Fall 2018;
\item[-] instructor of MATH 345 - Differential Equations (Honors option), Colorado State University, Spring 2018;
\item[-] (graduate) lecture course on Determinantal Point Processes and Random Matrices, Colorado State University, Fall 2017;
\item[-] instructor of MATH 317 - Advanced Calculus of one variable, Colorado State University, Fall 2017;
\item[-] instructor of MATH 369 - Linear Algebra I, Colorado State University, Spring 2017;
\item[-] instructor of MATH 205 - Differential and Integral Calculus II, Concordia University, Winter 2011 and Fall 2011;
\item[-] teaching assistant of MATH 201 - Elementary Functions, Concordia University, Fall 2013;
\item[-] technical assistant of WeBWorK for the courses MATH 200, 201, 202, 203, 204, 205, Concordia University, Fall 2012 - Summer 2014;
\item[-] tutor at Math Help Center, Concordia University, Fall 2010 and Fall 2013. \\
 \end{itemize}

  
  \section{Student supervision}
  \begin{itemize} \itemsep -2pt  % reduce space between items
 \item[-] coordinator of one student for the Honors Option in the course MATH 345, Colorado State University, Spring 2018.\\
 \end{itemize}





\section{Languages}
%\ Italian (mother tongue), English (advanced), French (upper intermediate), Farsi (beginner).
\begin{itemize}
\item[-] Italian (mother tongue) \\
\item[-] English (level C1\footnote{Classification based upon the Common European Framework of Reference (CEFR)}, advanced) \vspace{2mm}   \\ 
 \emph{International English Language Testing System (IELTS)} \\
result (1/2010): 7/9 \\
written comprehension: 8/9 -- written production: 7/9\\
oral comprehension: 7/9 -- oral production: 6.5/9\\ 
British Council, Italy. \\
\item[-] French (level B2$^\dagger$, upper intermediate) \vspace{2mm}   \\ 
 \emph{Connaissance de la langue Fran\c{c}aise DELF} \\
 result (1/2016): 79/100 \\
written comprehension: 22.50/25 -- written production: 15,50/25\\
oral comprehension: 21.00/25 --  oral production: 20.00/25\\ 
Alliance Fran\c{c}aise de Bruxelles-Europe, Belgium.   \\
\item[-] Persian (level A1$^\dagger$, beginner)\\
\item[-] Dutch (level A1$^\dagger$, beginner)
\end{itemize}




 
% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer Skills}
 
   \begin{tabular}{l p{4in}}
    \underline{Languages:} & C++, HTML, Python, R.\\
     \underline{Software:} &  WebWork, MatLab, Latex, Maple.\\%, Microsoft Office. \\
 \end{tabular}
 
  \section{Leadership and organizational activities}

\begin{itemize}\itemsep -2pt
%\item Volunteer at Exposcience - Stewart Hall Science \& Technology Exhibition (Concordia University), November 2012 and November 2013, Pointe-Claire (QC).
%%I suggested and created an installation inspired by the Seven Bridges of K\"onigsberg, in order to teach graph theory at a very elementary and intuitive level. The installation was later used also during high-school lectures by MTM (Master in Teaching Mathematics) students of Concordia.
%\item Volunteer for the project ``Test di usabilit\`a sulla Biblioteca Digitale dell'Universit\`a degli Studi di Milano" (test of usability on the Digital Library of the University of Milano), Divisione Coordinamento delle Biblioteche, University of Milano, May 2010;
%\item Volunteer at the event amfAR Milano 2009, amfAR - The Foundation for AIDS research, September 2009.
%\end{itemize}
%
%
%\begin{itemize}
\item[-]  {\bf 09/2011--10/2013:} president of the Mathematics and Statistics Graduate Students Association (MASGSA), Concordia University;
\item[-] {\bf 09/2012--04/2013:} organizer of the Graduate Students Seminar series, Concordia University;
%As President of MASGSA, I was working on the following activities: organizing social events and Students Seminars, designing and keeping constantly updated a website for MASGSA association (masgsaconcordia.tk), supporting new admitted and returning students (in particular, taking care of the financial situation of international students; for many of them it is rather critic, since Concordia financial support is too low to afford both international tuition and basic living expenses).
\item[-] {\bf 05/2012--04/2013:} member of the Departmental Appraisal Committee (DAC) as Graduate Students Representative at the Department of Mathematics and Statistics, Concordia University;
\item[-] {\bf 09/2015--10/2016:} organizer of seminar series of the Mathematical Physics group, UC Louvain. \\
\end{itemize}


 \section{Volunteer experiences}

\begin{itemize}\itemsep -2pt
\item[-]  {\bf 09/2009:} volunteer at the event amfAR Milano 2009, amfAR - The Foundation for AIDS research.
\item[-] {\bf 09/2009--08/2010:} part of the Schola Gregoriana Mediolanensis (gregorian choir), Milano (Italy).
\item[-]  {\bf 05/2010:} volunteer for the project ``Test di usabilit\`a sulla Biblioteca Digitale dell'Universit\`a degli Studi di Milano" (test of usability on the Digital Library of the University of Milano), Universit\`a degli Studi di Milano.
\item[-] {\bf 01/2011--04/2014:} part of the Concordia University Choir, Concordia University.
\item[-]  {\bf 11/2012 and 11/2013:} creator and organizer of the Mathematics installations at Exposcience - Stewart Hall Science \& Technology Exhibition (Concordia University), Pointe-Claire (QC, Canada).
%I suggested and created an installation inspired by the Seven Bridges of K\"onigsberg, in order to teach graph theory at a very elementary and intuitive level. The installation was later used also during high-school lectures by MTM (Master in Teaching Mathematics) students of Concordia.
\item[-] {\bf 10/2014--10/2016:} part of Stella Matutina (gregorian choir), Bruxelles (Belgium).
\item[-] {\bf 11/2017:} volunteer for Math Day 2017, Colorado State University.
\item[-] {\bf 02/2017--10/2017 and 08/2018--now:} volunteer at the nonprofit restaurant FoCo Cafe, Fort Collins (CO).
\end{itemize}

 \section{Other interests}
 
singing, sailing, skiing, cooking.


 
 

\end{resume} 
\end{document} 



